---
title: "Activity5"
output: html_document
---

1.	The R codes that will store the data from the AsULearn file StudentProfile.csv in a data frame called designdata, display the first few rows of the data frame and count the number of cases.

```{r}
StudentProfile <- read.csv("StudentProfile.csv")
designdata<- data.frame(StudentProfile)
head(designdata) #Prints the first part of table.
nrow(designdata) #Counts Number of Cases(Number of Rows)
```

2.	The R codes for a function that will randomly select about half of the experimental units stored in a vector x, assigns them to treatment 1 and then assigns the remaining experimental units to treatment 2.  The output of the function should display the entries of the vector that are assigned to each of the two treatments.    

```{r}
myfunction <- function(x) {
  df.1 <<- data.frame(matrix(x, nrow = length(x)/2))
  names(df.1) <- gsub("X", "Treatment", names(df.1), fixed = "TRUE")
  return(sample(df.1))
}

```



3.	The R codes that use the function in #2 to randomly assign the students in the data frame to two treatments.    The output of the R codes should display the names assigned to each of the two treatments.    

```{r}
myfunction(designdata$Student)



```

4. A paragraph discussing why the method of assigning the students to the two treatments  in #3 is called Completely Randomized Design

This is a completely randomized design because the subjects are randomly assigned to the treatments. The same number of subjects are assigned to each of the two treatments. A completely randomized design relies oin randomization to control for the effects of extraneous variables. It is an assumption that, on average, extraneous factors will affect treatment conditions equally; so any differences between the conditions can fairly be attributed to the independent variable.


5.	The R codes that will help you answer which of the two treatment groups in #3 contain more A students.   The R codes should display the answer together with a supporting graph and/or statistics. 

```{r}
Treatment1<- designdata$Student[c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15)]
Treatment2<- designdata$Student[c(16,17,18,19,20,21,22,23,24,25,26,27,28,29,30)]
randomTreatment1<- sample(Treatment1)
randomTreatment2<- sample(Treatment2)
subset(randomTreatment1, designdata$Grade =="A")
subset(randomTreatment2, designdata$Grade =="A")



```
6

